---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Bryan baby stats

Romain Francois's family just welcomed a new addition and he [tweeted a photo of those first few days](https://twitter.com/romain_francois/status/886502077492539394), where baby's trying to get back to their birthweight. It reminded me that I kept records of how much formula our twins were drinking for the first few months. I even made a figure for their baby book. Now ... where did I put all that?

I managed to find the folder, last opened in December 2006, complete with "2006 Jenny" R code and some figures. Would the code still run!?! I had to fix one thing:

  * Change absolute paths to relative, because my filesystem is set up differently now. Use the [here](https://krlmlr.github.io/here/) package people!

My code had zero dependencies, other than R itself, which is why this little exercise went so well.
  
I got the same PDFs back! That 2006 code is found in [makeFigures.r](makeFigures.r). In hindsight, I must have executed specific lines selectively to develop the plot and then store in different figure formats, because the code for `x11()`, `png()`, and `pdf()` is all up in each others' business. Remember, I *was* sleep deprived.

Below I render the 2006 code, with relative paths and a few well-placed `#`s added, so we get inline figures.

## `makeFigures.r`

```{r formulaIntake}
fIntake <-
  read.csv("formulaIntake.csv")

#x11(width = 6* 2.5, height = 4*2.5)
jMult <- 200
#png("formulaIntake.png",
#     width = 6 * jMult, height = 4 * jMult, res = 200)
#     quality = 100)

#pdf("formulaIntake.pdf",
#    width = 6, height = 4, family = "Times")
par(las = 1, mar = c(1, 6, 3, 0.5) + 0.1)
matplot(1:nrow(fIntake), fIntake[,c("Wesley","Eli")], type = "l",
        xlab = "", ylab = "", axes = FALSE, col = c(3,4),
        lty = "dashed", cex.main = 1.3,
        main = "Managing Inputs ... Nicer than Outputs")
lines(ksmooth(1:nrow(fIntake), fIntake$Wesley, "normal", bandwidth=5),
      col=3, lwd = 2)
lines(ksmooth(1:nrow(fIntake), fIntake$Eli, "normal", bandwidth=5),
      col=4,
      lwd = 2)
box()
mtext(side = 2, "Daily\nformula\nintake\nin ounces", line = 4, adj = 0.5)
mtext(c("February", "March", "April"), adj = 0,
      side = 1, line = 0, at = c(1,23,53))
axis(side = 2)
#     at = fIntake$Date[0:8 * 7 + 1],
#     at = c(1,23,53),
#     labels = c("February", "March", "April"),
#     tick = FALSE)

legend(x = "bottomright",
       legend = c("Wesley","Eli"),
       col = c(3,4),  lwd = 2, bty = "n", cex = 1.3)

#dev.off()
```

```{r birthStats}
bStats <- read.table("birthStats.txt")

bData <- as.matrix(bStats[,c("WeightGms","LengthCm","HeadCm")])
bData <- bData / rep(colMeans(bData), each = 3)

#pdf("birthStats.pdf",
#    width = 6, height = 4, family = "Times")
par(las = 1)
foo <- barplot(bData,
               beside = T, horiz = T, xlim = c(0,1.8),
               main = "Bryan Kids' Birth Statistics",
               names.arg = c("Weight","Length","Head"),
               legend.text = c("Reed","Wesley","Eli"),
               col = c("tomato4","green3","slateblue3"), axes = FALSE)
text(bData[,1] + 0.025, foo[,1],
     labels = paste(bStats$WeightLbs,"lbs,",bStats$WeightOzs,"ozs"),
     adj = 0)
text(bData[,2] + 0.025, foo[,2],
     labels = paste(bStats$LengthIn,"inches"),
     adj = 0)
text(bData[,3] + 0.025, foo[,3],
     labels = paste(bStats$HeadIn,"inches"),
     adj = 0)

#dev.off()
```

